V4 Neural Network Model for Shape-based Feature Extraction and Object Discrimination

### 2015-09-07 article.tex
refine some figures

The HMAX model \cite{cadieu2007} and the deep learning model \cite{bengio2009}, which both draw inspiration from the neural systems, 
construct similar multilayer structures.
In particular, the deep model exhibits high performance in classifying very large image database \cite{krizhevsky2012}.
However, a deep model is a neural network of very large scale (In \cite{krizhevsky2012}, the network has 8 layers and more than 400,000 neurons),
and training such a model generally requires a large number of training samples (\cite{krizhevsky2012} uses 1.2 million training images).
Deep learning is a process of fully automatic feature extraction.
Limited training samples can not provide enough variety to keep the model from over-fitting.
The HMAX model consists of fewer layers and only one layer (S2 layer) is trainable, which allows the model to work on limited train samples.
In our proposed model, we combine these two approach.
With prior knowledge of the cortical neurons, we manually design the layers corresponding to the primary visual cortex
and V4 features are automatically extracted based on the output of the artificially designed network.
This strategy saves us from retraining the first layers every time.
Additionally, we implement a layer of saliency filters to detect key-points in images,
which enables our model to process images of various sizes efficiently. 
In \tablename~\ref{tab:2}, we summarize the comparison of the three models.

Future work should involve further investigation into the visual systems and extensive evaluation on shape-based object detection.
Currently the model extracts only shape-based features.
Information about color and texture is also very important, which should also participate in the process of visual recognition.
The proposed model is a feed-forward network.
We should also consider the function of feedback connections in the neural systems.
These show the direction of our future work.

>>>>

The HMAX model \cite{cadieu2007} and the deep learning model \cite{bengio2009}, which both draw inspiration from the neural systems, 
construct similar multilayer structures.
In particular, the deep model exhibits high performance in classifying very large image database \cite{krizhevsky2012}.
However, a deep model is a neural network of very large scale (In \cite{krizhevsky2012}, the network has 8 layers and more than 400,000 neurons),
and training such a model generally requires a large number of training samples (\cite{krizhevsky2012} uses 1.2 million training images).
Deep learning is a process of fully automatic feature extraction.
Limited training samples can not provide enough variety to keep the model from over-fitting.
The HMAX model consists of fewer layers and only one layer (S2 layer) is trainable, which allows the model to work on limited training samples.
In the proposed model, we combine these two approaches.
The layers corresponding to the primary visual cortex is artificially designed with prior knowledge of the cortical neurons.
V4 features are automatically extracted based on the output of the artificially designed network.
This strategy saves us from retraining the first layers every time.
Additionally, we implement a layer of saliency filters to detect key-points in images,
which enables the model to process images of various sizes efficiently. 
In \tablename~\ref{tab:2}, we summarize the comparison of the three models.

Future work should involve further investigation into the visual systems and extensive evaluation on shape-based object detection.
